---
output:
  html_document:
    highlight: null
    css: style.css
    self_contained: no
    keep_md: true
---

```{r, echo=FALSE}
library(stringr)

date <- "9/28/2017"
vendor <- "Good Earth Catering Company"
title <- "Fall 2017 Meet and Greet"
speaker <- "Fall 2017 Schedule"
department <- "Masters in Computational Social Science"
university <- "University of Chicago"
github_home <- "https://github.com/uchicago-computation-workshop"
short_title_n = 3


```

```{r, echo=FALSE}
#Function to Shorten Title
small_title <- function(x, n=3) {
  ul <- unlist(strsplit(x, split = "\\s+"))[1:n]
  paste(ul,collapse=" ")
}

#Characters
unwanted_array = list(    'Š'='S', 'š'='s', 'Ž'='Z', 'ž'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Å'='A', 'Æ'='A', 'Ç'='C', 'È'='E', 'É'='E',
                            'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ø'='O', 'Ù'='U',
                            'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'å'='a', 'æ'='a', 'ç'='c',
                            'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                            'ö'='o', 'ø'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )


#Year
year <- substr(date, nchar(date)-4+1, nchar(date))

#Author Name
author_clean_lower <- str_replace_all(str_to_lower(speaker), " ", "_")

#Remove Unwanted Characters
out <- author_clean_lower
for(i in seq_along(unwanted_array))
    out <- gsub(names(unwanted_array)[i],unwanted_array[i],out)
author_clean <- out
author_lastname <- tail(strsplit(author_clean,split="_")[[1]],1)

#Repository Name
#repo = paste(year, author_clean, sep = "_")
repo = author_clean
issues_page <- paste(github_home, repo, "issues", sep="/")

#Create File Name Parts
short_title <- small_title(title, short_title_n)
paper_file <- paste(year, author_lastname, short_title, sep="  ")

#Clean Up File Name
punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'

#Remove Punctuation
lowered_name <- str_to_lower(paper_file)
stripped_name <- str_replace_all(lowered_name, punct, "")
cleaned_name <- str_replace_all(stripped_name, " ", "_")
cleaned_paper_file <- paste(cleaned_name, "pdf", sep=".")

#File Name Link
paper_link = paste(github_home, repo, "blob/master", cleaned_paper_file, sep="/"  )


#Clean Short Title
short_title_clean <- str_replace_all(short_title, punct, "")

```

<br>

<h3 class=pfblock-header> The Spring 2019 </h3>
<h2 class=pfblock-header4> <a href="https://macss.uchicago.edu/content/computation-workshop"> Computational Social Science Workshop </a> </h2>
<br>
<h3 class=pfblock-header3> Thursday's, 11:00am-12:20pm, Kent 120 </h3>
<h5 class=pfblock-header3>A light lunch will be provided at each workshop.</h5>
<br>

<h3 class=pfblock-header4> April 4th </h3>
<h3 class=pfblock-header4> Co-sponsored by the Quantitative Methods Committee </h3>
<h3 class=pfblock-header4><a href="https://www.american.edu/cas/faculty/agolan.cfm"> Amos Golan </a> </h3>
<h6 class=pfblock-header4>Professor of Economics, Director of the the Info-Metrics Institute</h6>
<h5 class=pfblock-header4>American University</h5>
<br>


<h3 class=pfblock-header4> April 11th </h3>
<h3 class=pfblock-header4><a href="http://www.amaatouq.com/"> Abdullah Almaatouq </a> </h3>
<h6 class=pfblock-header4> Ph.D. Student in Computational Science and Engineering, Research Assistant at the Human Dynamics Group </h6>
<h5 class=pfblock-header4>Massachusetts Institute of Technology (MIT)</h5>
<br>


<h3 class=pfblock-header4> April 25th </h3>
<h3 class=pfblock-header4><a href="https://genes.uchicago.edu/directory/andrey-rzhetsky-phd"> Andrey Rzhetsky </a> </h3>
<h6 class=pfblock-header4>Professor, Department of Medicine and Department of Human Genetics; Senior Fellow, Computation Institute; Senior Fellow, Institute for Genomics and Systems Biology</h6>
<h5 class=pfblock-header4>The University of Chicago</h5>
<br>


<h3 class=pfblock-header4> May 2nd </h3>
<h3 class=pfblock-header4><a href="https://www.teachersinsocialmedia.com/who-we-are"> Kaitlin Torphy, Ken Frank, Jiliang Tang </a> </h3>
<h6 class=pfblock-header4>Interdisciplinary Team of the "Teachers in Social Media Project"</h6>
<h5 class=pfblock-header4>Michigan State University</h5>
<br>


<h3 class=pfblock-header4> May 16th </h3>
<h3 class=pfblock-header4><a href="https://psych.princeton.edu/person/tom-griffiths"> Tom Griffiths </a> </h3>
<h6 class=pfblock-header4>Professor of Psychology and Cognitive Science</h6>
<h5 class=pfblock-header4>Princeton University</h5>
<br>


<h3 class=pfblock-header4> May 23rd </h3>
<h3 class=pfblock-header4><a href="https://pondside.uchicago.edu/oba/faculty/palmer_s.html"> Stephanie Palmer </a> </h3>
<h6 class=pfblock-header4>Assistant Professor, Department of Organismal Biology and Anatomy</h6>
<h5 class=pfblock-header4>The University of Chicago</h5>
<br>


<br>

---

<p class=footertext2> This weekly workshop highlights the work of those pioneering data science analytical techniques and social science and computation methods while bringing together graduate students, post-docs, and faculty all working at the nexus of computation and big, social science questions. The workshop also allows regular participants to share works in progress for feedback, fosters robust dialogue between young scholars in these emerging fields, and showcases local scholars leading pedagogical seminars on new papers or methods. </p>

<p class=footertext2> The 2018-2019 <a href="https://macss.uchicago.edu/content/computation-workshop"> Computation Workshop </a> meets each Thursday from 11:00 a.m. to 12:20 p.m. in Kent 120. All interested faculty and graduate students are welcome. Students in the Masters of Computational Social Science program are required to attend and join the discussion by posting a comment on the <a href="https://github.com/uchicago-computation-workshop/README"> issues page </a> of the <a href="https://github.com/uchicago-computation-workshop"> workshop's public repository on GitHub.</a></p>