---
output:
  html_document:
    highlight: null
    css: style.css
    self_contained: no
    keep_md: true
---

```{r, echo=FALSE}
library(stringr)

date <- "9/28/2017"
vendor <- "Good Earth Catering Company"
title <- "Fall 2017 Meet and Greet"
speaker <- "Fall 2017 Schedule"
department <- "Masters in Computational Social Science"
university <- "University of Chicago"
github_home <- "https://github.com/uchicago-computation-workshop"
short_title_n = 3


```

```{r, echo=FALSE}
#Function to Shorten Title
small_title <- function(x, n=3) {
  ul <- unlist(strsplit(x, split = "\\s+"))[1:n]
  paste(ul,collapse=" ")
}

#Characters
unwanted_array = list(    'Š'='S', 'š'='s', 'Ž'='Z', 'ž'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Å'='A', 'Æ'='A', 'Ç'='C', 'È'='E', 'É'='E',
                            'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ø'='O', 'Ù'='U',
                            'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'å'='a', 'æ'='a', 'ç'='c',
                            'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                            'ö'='o', 'ø'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )


#Year
year <- substr(date, nchar(date)-4+1, nchar(date))

#Author Name
author_clean_lower <- str_replace_all(str_to_lower(speaker), " ", "_")

#Remove Unwanted Characters
out <- author_clean_lower
for(i in seq_along(unwanted_array))
    out <- gsub(names(unwanted_array)[i],unwanted_array[i],out)
author_clean <- out
author_lastname <- tail(strsplit(author_clean,split="_")[[1]],1)

#Repository Name
#repo = paste(year, author_clean, sep = "_")
repo = author_clean
issues_page <- paste(github_home, repo, "issues", sep="/")

#Create File Name Parts
short_title <- small_title(title, short_title_n)
paper_file <- paste(year, author_lastname, short_title, sep="  ")

#Clean Up File Name
punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'

#Remove Punctuation
lowered_name <- str_to_lower(paper_file)
stripped_name <- str_replace_all(lowered_name, punct, "")
cleaned_name <- str_replace_all(stripped_name, " ", "_")
cleaned_paper_file <- paste(cleaned_name, "pdf", sep=".")

#File Name Link
paper_link = paste(github_home, repo, "blob/master", cleaned_paper_file, sep="/"  )


#Clean Short Title
short_title_clean <- str_replace_all(short_title, punct, "")

```

<br>

<h3 class=pfblock-header> The Winter 2019 </h3>
<h2 class=pfblock-header4> <a href="https://macss.uchicago.edu/content/computation-workshop"> Computation Workshop </a> </h2>
<br>
<h3 class=pfblock-header3> Thursday's, 11:00am-12:20pm, Kent 120 </h3>
<h5 class=pfblock-header3>A light lunch will be provided at each workshop.</h5>
<br>


<h3 class=pfblock-header4> January 10th </h3>
<h3 class=pfblock-header4><a href="https://psychology.uchicago.edu/directory/edward-s-awh"> Ed Awh </a> </h3>
<h6 class=pfblock-header4>Professor, Department of Psychology, The Institute for Mind and Biology, and the Grossman Institute for Neuroscience, Quantitative Biology and Human Behavior</h6>
<h5 class=pfblock-header4>The University of Chicago</h5>
<br>


<h3 class=pfblock-header4> January 17th </h3>
<h3 class=pfblock-header4><a href="https://www.linkedin.com/in/nicolas-masse-43806a1a/"> Nicolas Masse </a> </h3>
<h6 class=pfblock-header4>Postdoctoral Scholar and Staff Scientist, Department of Neurobiology</h6>
<h5 class=pfblock-header4>The University of Chicago</h5>
<br>


<h3 class=pfblock-header4> January 24th </h3>
<h3 class=pfblock-header4><a href="http://web.stanford.edu/~bonica/"> Adam Bonica </a> </h3>
<h6 class=pfblock-header4>Associate Professor of Political Science</h6>
<h5 class=pfblock-header4>Stanford University</h5>
<br>


<h3 class=pfblock-header4> February 14th </h3>
<h3 class=pfblock-header4><a href="http://monicarosenberg.org/"> Monica Rosenberg </a> </h3>
<h6 class=pfblock-header4>Postdoctoral Associate, Department of Psychology</h6>
<h5 class=pfblock-header4>Yale University</h5>
<br>

<h3 class=pfblock-header4> February 21st </h3>
<h3 class=pfblock-header4><a href="https://www.colorado.edu/neuroscience/tor-wager"> Tor Wager </a> </h3>
<h6 class=pfblock-header4>Professor of Psychology and Neuroscience, Director of the Cognitive and Affective Neuroscience Laboratory</h6>
<h5 class=pfblock-header4>University of Colorado Boulder</h5>
<br>

<h3 class=pfblock-header4> February 28th </h3>
<h3 class=pfblock-header4><a href="http://home.uchicago.edu/sdurlauf/index.html"> Steven Durlauf </a> </h3>
<h6 class=pfblock-header4>Steans Professor of Educational Policy at the Harris School of Public Policy Studies</h6>
<h5 class=pfblock-header4>The University of Chicago</h5>
<br>

<br>

---

<p class=footertext2> This weekly workshop highlights the work of those pioneering data science analytical techniques and social science and computation methods while bringing together graduate students, post-docs, and faculty all working at the nexus of computation and big, social science questions. The workshop also allows regular participants to share works in progress for feedback, fosters robust dialogue between young scholars in these emerging fields, and showcases local scholars leading pedagogical seminars on new papers or methods. </p>

<p class=footertext2> The 2018-2019 <a href="https://macss.uchicago.edu/content/computation-workshop"> Computation Workshop </a> meets each Thursday from 11:00 a.m. to 12:20 p.m. in Kent 120. All interested faculty and graduate students are welcome. Students in the Masters of Computational Social Science program are required to attend and join the discussion by posting a comment on the <a href="https://github.com/uchicago-computation-workshop/README"> issues page </a> of the <a href="https://github.com/uchicago-computation-workshop"> workshop's public repository on GitHub.</a></p>