---
output:
  html_document:
    highlight: null
    css: style.css
    self_contained: no
    keep_md: true
---

```{r, echo=FALSE}
library(stringr)

date <- "9/28/2017"
vendor <- "Good Earth Catering Company"
title <- "Fall 2017 Meet and Greet"
speaker <- "Fall 2017 Schedule"
department <- "Masters in Computational Social Science"
university <- "University of Chicago"
github_home <- "https://github.com/uchicago-computation-workshop"
short_title_n = 3


```

```{r, echo=FALSE}
#Function to Shorten Title
small_title <- function(x, n=3) {
  ul <- unlist(strsplit(x, split = "\\s+"))[1:n]
  paste(ul,collapse=" ")
}

#Characters
unwanted_array = list(    'Š'='S', 'š'='s', 'Ž'='Z', 'ž'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Å'='A', 'Æ'='A', 'Ç'='C', 'È'='E', 'É'='E',
                            'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ø'='O', 'Ù'='U',
                            'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'å'='a', 'æ'='a', 'ç'='c',
                            'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                            'ö'='o', 'ø'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )


#Year
year <- substr(date, nchar(date)-4+1, nchar(date))

#Author Name
author_clean_lower <- str_replace_all(str_to_lower(speaker), " ", "_")

#Remove Unwanted Characters
out <- author_clean_lower
for(i in seq_along(unwanted_array))
    out <- gsub(names(unwanted_array)[i],unwanted_array[i],out)
author_clean <- out
author_lastname <- tail(strsplit(author_clean,split="_")[[1]],1)

#Repository Name
#repo = paste(year, author_clean, sep = "_")
repo = author_clean
issues_page <- paste(github_home, repo, "issues", sep="/")

#Create File Name Parts
short_title <- small_title(title, short_title_n)
paper_file <- paste(year, author_lastname, short_title, sep="  ")

#Clean Up File Name
punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'

#Remove Punctuation
lowered_name <- str_to_lower(paper_file)
stripped_name <- str_replace_all(lowered_name, punct, "")
cleaned_name <- str_replace_all(stripped_name, " ", "_")
cleaned_paper_file <- paste(cleaned_name, "pdf", sep=".")

#File Name Link
paper_link = paste(github_home, repo, "blob/master", cleaned_paper_file, sep="/"  )


#Clean Short Title
short_title_clean <- str_replace_all(short_title, punct, "")

```

<br>

<h3 class=pfblock-header> The Fall 2018 </h3>
<h2 class=pfblock-header4> <a href="https://macss.uchicago.edu/content/computation-workshop"> Computation Workshop </a> </h2>
<br>
<h3 class=pfblock-header3> Thursday's, 11:00am-12:20pm, Kent 120 </h3>
<h5 class=pfblock-header3>A light lunch will be provided at each workshop.</h5>
<br>


<h3 class=pfblock-header4> October 5th </h3>
<h3 class=pfblock-header4> <a href="https://www.santafe.edu/people/profile/luis-bettencourt"> Luís M. A. Bettencourt </a> </h3>
<h6 class=pfblock-header4>Professor of Ecology and Evolution, Pritzker Director of the Mansueto Institute for Urban Innovation at the</h6>
<h5 class=pfblock-header4>University of Chicago</h5>
<br>


<h3 class=pfblock-header4> October 12th </h3>
<h3 class=pfblock-header4><a href="http://people.cs.uchicago.edu/~ravenben/"> Ben Zhao </a> </h3>
<h6 class=pfblock-header4>Neubauer Professor of Computer Science, Co-Director at the Systems, Algorithms, Networking, and Data Lab at the</h6>
<h5 class=pfblock-header4>University of Chicago</h5>
<br>


<h3 class=pfblock-header4> October 19th </h3>
<h3 class=pfblock-header4> TBD </h3>
<br>


<h3 class=pfblock-header4> October 26th </h3>
<h3 class=pfblock-header4><a href="http://cnets.indiana.edu/people/santo-fortunato/"> Santo Fortunato </a> </h3>
<h6 class=pfblock-header4>Professor in the School of Informatics and Computing, Director of the Center for Complex Networks and Systems Research at</h6>
<h5 class=pfblock-header4>Indiana University - Bloomington</h5>
<br>


<h3 class=pfblock-header4> November 2nd </h3>
<h3 class=pfblock-header4>TBD </h3>
<br>


<h3 class=pfblock-header4>November 9th </h3>
<h3 class=pfblock-header4><a href="https://www.asc.upenn.edu/people/faculty/damon-centola-phd"> Damon Centola </a> </h3>
<h6 class=pfblock-header4>Associate Professor in the Annenberg School for Communication, Director of the Network Dynamics Group at the</h6>
<h5 class=pfblock-header4>University of Pennsylvania</h5>
<br>


<h3 class=pfblock-header4>November 16th </h3>
<h3 class=pfblock-header4><a href="https://humdev.uchicago.edu/directory/guanglei-hong"> Guanglei Hong </a> </h3>
<h6 class=pfblock-header4>Associate Professor of Comparative Human Development, Executive Committee for Computational Social Science at the</h6>
<h5 class=pfblock-header4>University of Chicago</h5>
<br>


<br>

---

<p class=footertext2> This weekly workshop highlights the work of those pioneering data science analytical techniques and social science and computation methods while bringing together graduate students, post-docs, and faculty all working at the nexus of computation and big, social science questions. The workshop also allows regular participants to share works in progress for feedback, fosters robust dialogue between young scholars in these emerging fields, and showcases local scholars leading pedagogical seminars on new papers or methods. </p>

<p class=footertext2> The 2017-2018 <a href="https://macss.uchicago.edu/content/computation-workshop"> Computation Workshop </a> meets each Thursday from 11:00 a.m. to 12:20 p.m. in Kent 120. All interested faculty and graduate students are welcome. Students in the Masters of Computational Social Science program are expected to attend and join the discussion by posting a comment on the <a href="https://github.com/uchicago-computation-workshop/README"> issues page </a> of the <a href="https://github.com/uchicago-computation-workshop"> workshop's public repository on GitHub.</a></p>