---
output:
  html_document:
    highlight: null
    css: style.css
    self_contained: no
    keep_md: true
---

```{r, echo=FALSE}
library(stringr)
date <- "10/03/2019"
vendor <- "N/A"
title <- "Fall 2019 Schedule"
speaker <- "Fall 2019 Schedule"
department <- "Masters in Computational Social Science"
university <- "University of Chicago"
github_home <- "https://github.com/uchicago-computation-workshop"
short_title_n = 3
```

```{r, echo=FALSE}
#Function to Shorten Title
small_title <- function(x, n=3) {
  ul <- unlist(strsplit(x, split = "\\s+"))[1:n]
  paste(ul,collapse=" ")
}
#Characters
unwanted_array = list(    'Š'='S', 'š'='s', 'Ž'='Z', 'ž'='z', 'À'='A', 'Á'='A', 'Â'='A', 'Ã'='A', 'Ä'='A', 'Å'='A', 'Æ'='A', 'Ç'='C', 'È'='E', 'É'='E',
                            'Ê'='E', 'Ë'='E', 'Ì'='I', 'Í'='I', 'Î'='I', 'Ï'='I', 'Ñ'='N', 'Ò'='O', 'Ó'='O', 'Ô'='O', 'Õ'='O', 'Ö'='O', 'Ø'='O', 'Ù'='U',
                            'Ú'='U', 'Û'='U', 'Ü'='U', 'Ý'='Y', 'Þ'='B', 'ß'='Ss', 'à'='a', 'á'='a', 'â'='a', 'ã'='a', 'ä'='a', 'å'='a', 'æ'='a', 'ç'='c',
                            'è'='e', 'é'='e', 'ê'='e', 'ë'='e', 'ì'='i', 'í'='i', 'î'='i', 'ï'='i', 'ð'='o', 'ñ'='n', 'ò'='o', 'ó'='o', 'ô'='o', 'õ'='o',
                            'ö'='o', 'ø'='o', 'ù'='u', 'ú'='u', 'û'='u', 'ý'='y', 'ý'='y', 'þ'='b', 'ÿ'='y' )
#Year
year <- substr(date, nchar(date)-4+1, nchar(date))
#Author Name
author_clean_lower <- str_replace_all(str_to_lower(speaker), " ", "_")
#Remove Unwanted Characters
out <- author_clean_lower
for(i in seq_along(unwanted_array))
    out <- gsub(names(unwanted_array)[i],unwanted_array[i],out)
author_clean <- out
author_lastname <- tail(strsplit(author_clean,split="_")[[1]],1)
#Repository Name
#repo = paste(year, author_clean, sep = "_")
repo = author_clean
issues_page <- paste(github_home, repo, "issues", sep="/")
#Create File Name Parts
short_title <- small_title(title, short_title_n)
paper_file <- paste(year, author_lastname, short_title, sep="  ")
#Clean Up File Name
punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'
#Remove Punctuation
lowered_name <- str_to_lower(paper_file)
stripped_name <- str_replace_all(lowered_name, punct, "")
cleaned_name <- str_replace_all(stripped_name, " ", "_")
cleaned_paper_file <- paste(cleaned_name, "pdf", sep=".")
#File Name Link
paper_link = paste(github_home, repo, "blob/master", cleaned_paper_file, sep="/"  )
#Clean Short Title
short_title_clean <- str_replace_all(short_title, punct, "")
```

<br>

<h3 class=pfblock-header> The Fall 2019 </h3>
<h2 class=pfblock-header4> <a href="https://macss.uchicago.edu/content/computation-workshop"> Computation Workshop </a> </h2>
<br>
<h3 class=pfblock-header3> Thursday's, 11:00am-12:20pm, Hinds Laboratory 101 </h3>
<h5 class=pfblock-header3>A light lunch will be provided at each workshop.</h5>
<br>


<h3 class=pfblock-header4> October 3rd </h3>
<h3 class=pfblock-header4><a href="https://github.com/uchicago-computation-workshop/fall2019mixer"> CSS Mixer with Faculty </a> </h3>
<br>


<h3 class=pfblock-header4> October 10th </h3>
<h3 class=pfblock-header4><a href="https://github.com/uchicago-computation-workshop/BigDataMedicine"> Big Data in medicine </a> </h3>
<h6 class=pfblock-header4>A panel of distinguished University of Chicago faculty chaired by <a href="https://www.hopkinshistoryofmedicine.org/content/jeremy-greene">Jeremy Greene</a>, a renowned historian of medicine</h6>
<h3 class=pfblock-header4>4:00-5:20 PM | Location TBD</h5>
<br>

<h3 class=pfblock-header4> October 17th </h3>
<h3 class=pfblock-header4><a href="https://macss.uchicago.edu/directory/james-evans"> James Evans </a> </h3>
<h6 class=pfblock-header4>Professor of Sociology, Director of the Knowledge Lab, Faculty Director of the Masters Program in Computational Social Science, and External Professor at the Santa Fe Institutee</h6>
<h5 class=pfblock-header4>The University of Chicago</h5>
<br>


<h3 class=pfblock-header4>October 24th </h3>
<h3 class=pfblock-header4><a href="https://fredturner.stanford.edu/"> Fred Turner </a> </h3>
<h6 class=pfblock-header4>Professor of Communication </h6>
<h5 class=pfblock-header4>Stanford University</h5>
<br>


<h3 class=pfblock-header4>October 31st </h3>
<h3 class=pfblock-header4> TBD </h3>
<br>

<h3 class=pfblock-header4>November 7th </h3>
<h3 class=pfblock-header4> TBD </h3>
<br>

<h3 class=pfblock-header4>November 14th </h3>
<h3 class=pfblock-header4> TBD </h3>
<br>

<h3 class=pfblock-header4>November 21st </h3>
<h3 class=pfblock-header4> TBD </h3>
<br>


---

<p class=footertext2> This weekly workshop highlights the work of those pioneering data science analytical techniques and social science and computation methods while bringing together graduate students, post-docs, and faculty all working at the nexus of computation and big, social science questions. The workshop also allows regular participants to share works in progress for feedback, fosters robust dialogue between young scholars in these emerging fields, and showcases local scholars leading pedagogical seminars on new papers or methods. </p>

<p class=footertext2> The 2019-2020 <a href="https://macss.uchicago.edu/content/computation-workshop"> Computation Workshop </a> meets each Thursday from 11:00 a.m. to 12:20 p.m. All interested faculty and graduate students are welcome. Students in the Masters of Computational Social Science program are required to attend and join the discussion by posting a comment on the <a href="https://github.com/uchicago-computation-workshop/README"> issues page </a> of the <a href="https://github.com/uchicago-computation-workshop"> workshop's public repository on GitHub.</a></p>
